Lattice model

### 2017-04-03 oopsla17/lattice-model.tex
Remove origin redfinition again
Connecting lemma

\todo{%
  Definition of origin is not needed.

  \begin{defn}{(Origin)}
    In $N$-dimensions, the \emph{origin} $\mathbf{0}_N$ is the singleton set
    $\{0^N\}$, or equivalently the vector of unit intervals $\interv{0}{0}{N}$.
  \end{defn}
}

@@

\begin{lem}
  The following three statements are equivalent for a set of points $P \subseteq
  \mathbb{Z}^N$:
%
  \begin{enumerate}
    \item $P$ defines a superposition of hyper-rectangles each of which crosses
      the extended origin;
    \item $P$ is the same as its exact set $\mathit{ES}_P$;
    \item $P$ when regarded as offsets from induction variables forms a
      neighbourhood stencil;
    \item $P$ is a subset of \region{N}.
  \end{enumerate}
\end{lem}

>>>>

@@

\begin{lem}{(\emph{Connecting})}
  The following three statements are equivalent for a set of points $P \subseteq
  \mathbb{Z}^N$:
%
  \begin{enumerate}
    \item $P$ defines a superposition of hyper-rectangles each of which crosses
      the extended origin;
    \item $P$ is the same as its exact set $\mathit{ES}_P$;
    \item $P$ when regarded as offsets from induction variables forms a
      neighbourhood stencil;
    \item $P$ is a subset of \region{N}.
  \end{enumerate}
\end{lem}
